### 2010-03-19 papers/icfp-2010-desc/paper_idesc.tex
Desc@ICFP: a tagged indexed description is a I -> IDesc I in becoming. Fix FreeIMonad construction. Fix usages of HExprFreeD.
Desc@ICFP: fix typos. Clean-up solved \notes.
Desc@ICFP: fix typo for evalOne

\note{the big square brackets should be red (pwm: use \\bigRedBracket :)) }

@@

\[\stk{
\evalOne : \PI{\V{ty}}{\Ty} \idescop{\toIDesc{\HExprD}}{\Ty}{ty} \To {\Val{ty}} \\
\begin{array}{@{}l@{\:=\:\:}l}
\evalOne\: \_\: \pair{\Eval{}}{x}{}                                         & x \\
\evalOne\: \_\: \pair{\Econd{}{}{}}{\pair{\BoolTrue}{\pair{x}{\_}{}}{}}{}   & x \\
\evalOne\: \_\: \pair{\Econd{}{}{}}{\pair{\BoolFalse}{\pair{\_}{y}{}}{}}{}  & x \\
\evalOne\: \Enat\: \pair{\Eplus{}{}}{\pair{x}{y}{}}{}                       & \F{plusHost}\: x y \\
\evalOne\: \Ebool\: \pair{\Ele{}{}}{\pair{x}{y}{}}{}                        & \F{leHost}\: x y 
\end{array} \\
\\
\evalH : \PI{\V{ty}}{\Ty} 
           \IMu{\Ty}{\toIDesc{\HExprD}}{ty} \To
           \Val{ty} \\
\evalH\: ty\: term = \F{cataI}\: \Ty\: 
                                 \toIDesc{\HExprD}\: 
                                 \Val{}\: 
                                 \evalOne\: 
                                 ty\: 
                                 term
}\]
\note{pwm: $\evalOne$ rather illustrates my point about the 2 types of IFunc
floating around, $\idescop{\_}{}{}$ is defined using the 1st notion, and used it
here as if it were the 2nd}

@@

Consequently, replacing $\Val{ty}$ by
$(\SUM{\Val{ty}}{\Var{dom}{ty}})$ in Figure~\ref{fig:hexpr-full} turns
the language of closed term into a language of opened terms with
constants. For readability, we will abbreviate $\LAM{ty}
\SUM{\Val{ty}{\Var{dom}{ty}}}$ into $\SUM{\Val{}}{\Var{}{}}$ \note{Is
  it polite and comprehensible to ask that?} This defines a new
indexed description, called $\HExprVarD{dom}$.

@@

\[\stk{
\begin{array}{ll}
\FreeIMonad{\_}{} : & \PITEL{\V{I}}{\Set}
                      \PITEL{\V{X}}{\V{I} \To \Set} \\
                    & \PITEL{\V{R}}{\V{I} \To \TagIDesc{I}} \To
                      (\V{I} \To \TagIDesc{I})
\end{array} \\
\FreeIMonad{R}{I}{X} \mapsto
    \LAM{i}
    \pair{\ListCons{\DVar{}}{(\fst{(R\: i)})}}
         {\pair{(\DConst{X\: i})}
               {(\snd{(R\: i)})}{}}{}
}\]

@@

\[
\begin{array}{@{}ll}
\substI : & \PITEL{\V{I}}{\Set}
            \PITEL{\V{X}, \V{Y}}{\V{I} \To \Set}
            \PITEL{\V{R}}{\V{I} \To \TagIDesc{\V{I}}} \\
          & \PITEL{\V{\sigma}}{\PI{\V{i}}{\V{I}} \V{X}\:\V{i} \To 
                               \IMu{I}{(\FreeIMonad{\V{R}}{\V{I}}{\V{Y}})}{\V{i}}} \\
          & \PITEL{\V{i}}{\V{I}}
            \PITEL{\V{D}}{\IMu{I}{(\FreeIMonad{\V{R}}{\V{I}}{\V{X}})}{\V{i}}} \To
            \IMu{I}{(\FreeIMonad{\V{R}}{\V{I}}{\V{Y}})}{\V{i}}
\end{array}
\]

>>>>

@@

\[\stk{
\evalOne : \PI{\V{ty}}{\Ty} \idescop{\toIDesc{\HExprD}\: ty}{\Ty}{ty} \To {\Val{ty}} \\
\begin{array}{@{}l@{\:=\:\:}l}
\evalOne\: \_\: \pair{\Eval{}}{x}{}                                         & x \\
\evalOne\: \_\: \pair{\Econd{}{}{}}{\pair{\BoolTrue}{\pair{x}{\_}{}}{}}{}   & x \\
\evalOne\: \_\: \pair{\Econd{}{}{}}{\pair{\BoolFalse}{\pair{\_}{y}{}}{}}{}  & x \\
\evalOne\: \Enat\: \pair{\Eplus{}{}}{\pair{x}{y}{}}{}                       & \F{plusHost}\: x y \\
\evalOne\: \Ebool\: \pair{\Ele{}{}}{\pair{x}{y}{}}{}                        & \F{leHost}\: x y 
\end{array} \\
\\
\evalH : \PI{\V{ty}}{\Ty} 
           \IMu{\Ty}{\toIDesc{\HExprD}}{ty} \To
           \Val{ty} \\
\evalH\: ty\: term = \F{cataI}\: \Ty\: 
                                 \toIDesc{\HExprD}\: 
                                 \Val{}\: 
                                 \evalOne\: 
                                 ty\: 
                                 term
}\]
\note{pwm: $\evalOne$ rather illustrates my point about the 2 types of
  IFunc floating around, $\idescop{\_}{}{}$ is defined using the 1st
  notion, and used it here as if it were the 2nd. pierre: in this
  case, it was a typo. But you're right, there is two notions and we
  probably want to clarify where these things live.}

@@

Consequently, replacing $\Val{ty}$ by
$(\SUM{\Val{ty}}{\Var{dom}{ty}})$ in Figure~\ref{fig:hexpr-full} turns
the language of closed term into a language of opened terms with
constants. For readability, we will abbreviate $\LAM{ty}
\SUM{\Val{ty}}{\Var{dom}{ty}}$ into $\SUM{\Val{}}{\Var{}{}}$ \note{Is
  it polite and comprehensible to ask that?} This defines a new
indexed description, called $\HExprVarD{dom}$.

@@

\[\stk{
\begin{array}{ll}
\FreeIMonad{\_}{} : & \PITEL{\V{I}}{\Set}
                      \PITEL{\V{X}}{\V{I} \To \Set} \\
                    & \PITEL{\V{R}}{\TagIDesc{I}} \To
                      \TagIDesc{I}
\end{array} \\
\FreeIMonad{(E,F)}{I}{X} \mapsto
    \pair{\pair{\ListCons{\DVar{}}{(\fst{E})}} 
               {\LAM{i}
                \pair{(\DConst{(X\: i)})}
                     {((\snd{E})\: i)}{}}{}}
         {F}{}
}\]

@@

\[
\begin{array}{@{}ll}
\substI : & \PITEL{\V{I}}{\Set}
            \PITEL{\V{X}, \V{Y}}{\V{I} \To \Set}
            \PITEL{\V{R}}{\TagIDesc{\V{I}}} \\
          & \PITEL{\V{\sigma}}{\PI{\V{i}}{\V{I}} \V{X}\:\V{i} \To 
                               \IMu{I}{(\FreeIMonad{\V{R}}{\V{I}}{\V{Y}})}{\V{i}}} \\
          & \PITEL{\V{i}}{\V{I}}
            \PITEL{\V{D}}{\IMu{I}{(\FreeIMonad{\V{R}}{\V{I}}{\V{X}})}{\V{i}}} \To
            \IMu{I}{(\FreeIMonad{\V{R}}{\V{I}}{\V{Y}})}{\V{i}}
\end{array}
\]
